---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# ```tlemix```

<!-- badges: start -->
[![CRAN version](https://www.r-pkg.org/badges/version/fsdaR)](https://cran.r-project.org/package=tlemix)
[![downloads](https://cranlogs.r-pkg.org/badges/fsdaR)](https://cran.r-project.org/package=tlemix)
[![license](https://img.shields.io/badge/license-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)
<!-- badges: end -->


The package `tlemix` implements a general framework for robustly fitting
discrete mixtures of regression models in the `R` statistical
computing environment. It implements the FAST-TLE algorithm
and uses the `R` package `FlexMix` as a computational engine for
fitting mixtures of general linear models (GLMs) and 
model-based clustering in R.

    
## Installation

The `tlemix` package is on CRAN (The Comprehensive R Archive Network) and the latest release can be easily installed using the command

```
install.packages("tlemix")
```

## Building from source

To install the latest stable development version from GitHub, you can pull this repository and install it using

```
## install.packages("remotes")
remotes::install_github("valentint/tlemix")
```

Of course, if you have already installed `remotes`, you can skip the first line (I have commented it out).  

## Example

This are three basic examples which show you if the package is properly installed:

```{r example1}
library(tlemix)

##  Mixture of two standard normal distributions with outliers.

data(gaussData)
str(gaussData)

## The example needs some computing time:

## estimate
est.tle <- TLE(y~x,"gaussian",data=gaussData,Density=flexmix.Density,
           Estimate=flexmix.Estimate,msglvl=1,nc=2,class="hard")

## plot data indicating clusters
tleplot(est.tle,gaussData,main="TLE Scatter Plot")

```
```{r example2}
library(tlemix)

##  Mixture of two standard normal distributions

data(McLachlan150)
str(McLachlan150)

## Th example needs some computing time:
d <- as.matrix(McLachlan150[,1:2])
est.tle <- TLE(d~1,"mvtnormal",data=d,Density=FLXmclust.Density,
           Estimate=FLXmclust.Estimate,msglvl=1,nc=3,class="hard")
tleplot(est.tle,as.data.frame(d),main="TLE Scatter Plot")

```

```{r example3}
library(tlemix)

##  Mixture two Poisson Regression Models

data(dPois)
str(dPois)

# The example needs some computing time:
est.tle <- TLE(y~x,"poisson",data=dPois,Density=flexmix.Density,
           Estimate=flexmix.Estimate,msglvl=1,nc=2,kTrim=200,class="hard")
tleplot(est.tle,dPois)

```
